A New Model to Predict Survival in Patients with End-Stage Liver Disease

### 2022-07-18 analysis/article.Rmd
feat: add author contributions and competing interests section

The study was supported by the AMPEL project ([www.ampel.care](https://www.ampel.care)).
This project is co-financed through public funds according to the budget
decided by the Saxon State Parliament under the
RL eHealthSax 2017/18 grant number 100331796.
The funder provided support in the form of
salaries for author SG
but did not have any additional role in the study design,
data collection and analysis, decision to publish, or preparation
of the manuscript.
We thank the whole AMPEL team for their support,
Stefan Kemnitz for his technical support regarding the use of the
HPC cluster of the University Greifswald and
Bernd Klaus for helpful discussions about survival analysis and proof reading the manuscript.

@@

>>>>

We thank the whole AMPEL team for their support,
Stefan Kemnitz for his technical support regarding the use of the
HPC cluster of the University Greifswald and
Bernd Klaus for helpful discussions about survival analysis and proof reading the manuscript.

@@

# Research funding

The study was supported by the AMPEL project ([www.ampel.care](https://www.ampel.care)).
This project is co-financed through public funds according to the budget
decided by the Saxon State Parliament under the
RL eHealthSax 2017/18 grant number 100331796.
The funder provided support in the form of
salaries for author SG
but did not have any additional role in the study design,
data collection and analysis, decision to publish, or preparation
of the manuscript.

# Author contributions

Funding was acquired by TK.
The study was conceptualised by SG and TK.
The data was acquired by TK.
The data was analysed and processed by SG.
Visualisation were produced by SG.
Original drafts of the manuscript were written by SG and TK.
Drafts were edited and reviewed by SG, TB, DS, BI, and TK.
The project was supervised by TK.
All authors have accepted responsibility for the entire content of this
manuscript and approved its submission.

# Competing interests

Authors state no conflict of interest.

# Informed consent

Informed consent was obtained from all individuals included in this study.

# Ethical approval

Research involving human subjects complied with all relevant national
regulations, institutional policies and is in accordance with the tenets of
the Helsinki Declaration (as revised in 2013), and has been
approved by the Ethics Committee at the Leipzig University Faculty of
Medicine (reference number: 039/14ff).
